Title Goes Here

### 2020-03-26 analysis/paper/paper.Rmd
gather data from SYG6

```{r}
# artifacts from SYG6 site

>>>>

```{r}

# artifacts from SYG6 site
SYG6_files <- dir(datadir, pattern = "SYG6_*")

ML = c()
BL = c()
TL = c()
SL = c()
MW = c()
TW = c()
SW = c()
for (i in 1:length(SYG6_files)) {
  filename <- paste(datadir, SYG6_files[i], sep = "")
  print(filename)
  landmarks <- read.tps(filename)
  ML <- c(ML, landmark_dist(landmarks, 1, 7))
  BL <- c(BL, bl_dist(landmarks))
  TL <- c(TL, tl_dist(landmarks))
  SL <- c(SL, sl_dist(landmarks))
  MW <- c(MW, landmark_dist(landmarks, 2, 11))
  TW <- c(TW, landmark_dist(landmarks, 3, 10))
  SW <- c(SW, landmark_dist(landmarks, 5, 8))
}
